Probabilistic Programming

### 2014-04-20 paper/paper.tex
Add abstract
Reflow paper to 80 chars wide
Add more sections to the paper

%\begin{abstract}
	%Your abstract goes here...
	%...
%\end{abstract}

@@

>>>>

\begin{abstract}
	We present Probabilistic Programming, a system for modeling abstract syntax
	trees of programs with markov chains, which we use to generate new programs.
	We attempt to use this as an assistive device to guide programmers through
	constructing JavaScript programs.
\end{abstract}

@@

\subsection{Modeling}

Representation of programs in a markov model

Other applications of the model: genetic algorithms

\subsection{Application}

The vim autocomplete script

The guided IDE

Design decisions, HCI factors

\section{Results}

\subsection{Using the IDE}

\subsection{Limitations of the IDE}

Usability issues

\subsection{Limitations of the model}

Choosing valid identifiers, matching identifiers

\section{Conclusions \& Open Problems}
